To run with the hare and hunt with the hounds: Optimal recommendation system with competing sellers. \\ Master Thesis

### 2020-05-21 Thesis.tex
Add files via upload
Thesis

\documentclass[a4paper]{article}
\usepackage[12pt]{extsizes} % 
\usepackage{setspace}
\doublespacing
\usepackage[utf8]{inputenc}
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{patterns}
\usepackage{setspace,amsmath}
\usepackage{mathtools}
\usepackage{pgfplots}
\usepackage[toc,page]{appendix}
\usepackage{titlesec}
%\usepackage{harvard}
\usepackage[round]{natbib}
\usepackage{pdfpages}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{amsthm}
\usepackage[shortlabels]{enumitem}
\usepackage{tikz}
\usepackage{multirow}
\usetikzlibrary{angles,quotes}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{breakcites}
\interfootnotelinepenalty=10000
\usepackage[makeroom]{cancel}
\usepackage{mathrsfs} % 
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
%\addto\captionsrussian{\renewcommand{\figurename}{Fig.}}
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools} 
\newcommand*{\hm}[1]{#1\nobreak\discretionary{}
{\hbox{$\mathsurround=0pt #1$}}{}}
\usepackage{graphicx}  % 
\graphicspath{{images/}{images2/}}  % 
\setlength\fboxsep{3pt} %  \fbox{} 
\setlength\fboxrule{1pt} % \fbox{}
\usepackage{wrapfig} % 
%\newenvironment{abstract}[0]{\small\rm
%	\begin{center}ABSTRACT
%		\\ \vspace{8pt}
%		\begin{minipage}{5.2in}\smalllineskip
%			\hspace{1pc}}{\end{minipage}\end{center}\vspace{-1pt}}
\newcommand{\prob}{\mathbb{P}}
\newcommand{\norma}{\mathcal{N}}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\summa}{\sum_{i=1}^n}
\usepackage[left=25mm, top=20mm, right=25mm, bottom=20mm, nohead, footskip=10mm]{geometry} % 
\usepackage{tikz} % 
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{definition}[theorem]{Definition}
%\let\cite = \citeasnoun
\title{To run with the hare and hunt with the hounds: Optimal recommendation system with competing sellers. \\ Master Thesis}
\date{}
\author{Danil Fedchenko}%\thanks{I am very grateful to: Sergei Izmalkov for constant help and support during the work on this project; Marta Troya Martinez for many valuable comments and suggestions. \newline Any remaining errors are mine.}}
\begin{document} 
	\maketitle
	\begin{abstract}
		Many e-commerce platforms that connect buyers and sellers employ recommender systems to help customers find products and services. These systems may have several potential effects on strategies of competing sellers: on one hand, more people become aware of products, so sellers may sell more goods and benefit from the presence of the recommender system. On the other hand, at the same time, more people become aware of the competitor seller. The latter effect may intensify the price competition and may hurt sellers but, of course, benefit customers. However, many platforms charge firms for sales and as a result have the stakes in firms profits. Thus, by designing the recommender policy the platform should balance the pro-competitive care about customers and anti-competitive incentives to keep high prices. The main goal of this work is to study this trade-off in details. I am solving for an optimal recommender policy and investigate factors that may affect it.
	\end{abstract}
\newpage
\tableofcontents
\newpage
	\section{Introduction}

		Suppose you came to New York and would like to find a good restaurant to go out tonight. Or you are going to spend your upcoming vacation on the coast of Spain and you need to find a hotel. Or you would like to buy something at your favorite online retailer. How would you proceed? What will be the first thing you interact with?  Before the World Wide Web, to find hotels or restaurants people relied upon guide-books and brochures distributed by travel agents. Those guides, once printed, usually quickly became out-of-date in the constantly changing environment, and could be criticized for containing misleading information.

@@

In the rows of examples, we should pay the special attention to online retailers such as \textit{Amazon}, \textit{eBay}, \textit{AliExpress} and many others. These platforms stand at the forefront of online Economics, generating huge amounts of money\footnote{e.g. \textit{Amazon}'s gross merchandise value (total value of goods sold on the platform) in 2019 fiscal year was \$335 billion.} and completely transforming the shopping experience for people all other the world. These platforms play roles of intermediaries between buyers and sellers, helping the buyers to find the goods they need. And this process clearly includes making recommendations: which seller to display the buyer when he or her is searching for something.

@@

For example, consider a retailer (such as \textit{Amazon} or \textit{eBay}), these retailers charge sellers commissions for each sale. These commissions usually take the form of a percentage commission \footnote{e.g. \textit{eBay} charges 8\% for each sale}. That means that the retailer obtains a higher profit if the price of the deal is higher. So, one of the questions that could potentially arise then is: should, in this case, the recommender system which \textit{Amazon} employs out of two sellers who sell (almost) substitutable goods recommend the one who has a higher price? Or suppose that \textit{eBay} is thinking on the commission rate it charges, %(now it is about 8\%),
 should the commission be set at the highest possible level that guarantees that sellers do not refrain from using the platform? What if, at the same time, the quality of goods may differ and the sellers may have an option to spend some resources on disclosing this quality (e.g. to make the detailed description or take high-resolution photos). Clearly the higher is the commission the less willing are the sellers to spend money on quality disclosure: cost does not outweigh benefits. But if sellers do not disclose the information this may adversely affect the customers' satisfaction since this may create a mismatch between buyers and sellers: people end up with the good which does not fit them well. Thus, thinking about commission rate the platform should take this aspect into account. Additionally, suppose that the recommendation system is not precise i.e. it sometimes makes mistakes on figuring out the customer's preferences. How does this inaccuracy affect the behavior (price setting) of competing sellers and how does it interact with their incentives to disclose the quality of their goods? What should be the optimal commissions and recommender policy in this case? Thus, in this work I am focusing on the following questions:
 \begin{itemize}
 	\item How does the presence of the recommender system which has stakes in sellers' profits affect competition and equilibrium behavior of sellers?
 	\item How does the rate of commission the platform charges sellers affect sellers' incentives to disclose information about their goods? What is the optimal rate of commission from the platform's standpoint?
 	\item How does the recommender system's precision affect competition and equilibrium behavior? And what should be the optimal precision?
 \end{itemize}

	To address these questions I build a theoretical one-period model. I consider a unit mass of heterogeneous customers whose preferences are summarized by the point on this unit line. At the extremes of the unit interval, there are two sellers. Customers demand one good and derive utility upon consuming the good but bear ``transportation'' cost by purchasing. This cost can be interpreted as the measure of quality of fit: how well the product fits the particular customer. The latter allows to treat the location of the customer as the customer's taste regarding the two goods offered by sellers: closer the customer is to the seller $A$ -- better the good of seller $A$ fits this customer, other things being equal.

@@

In the extension of the baseline model, I allow for the not perfectly precise recommender system, or in other words, I allow for some noise in evaluating customers' location. Namely, I assume that the signal, the platform receives reveals the true location of the customer only with some probability $\beta$, and with probability $1 - \beta$ the signal follows a uniform distribution. This has several consequences: first of all, clearly the platform should adjust its recommender strategy incorporating this inaccuracy. This adjustment manifests itself in the way how the platform treats and processes the signal regarding the location, now the platform takes into consideration that the signal could potentially be wrong. In this case, the best prediction of the customer's location the platform could made is simply an average location (since I model customers' location as uniform $(0, 1)$ random variable, an average location is $\frac{1}{2}$) . The latter effectively increases the share of customers in the middle of the unit interval, increasing incentives for sellers to undercut the competitor and to get access to this increased demand. Thus, the direct effect of the signal's inaccuracy intensifies the competition between sellers. This decreases the sellers' profits and as a result, decreases sellers' incentives to reveal the quality. At the same time, the recommender system's inaccuracy increases the attention the platform pays to the quality of the good when it makes recommendations: since the platform assumes that horizontal component (location) may be measured imprecisely, making a recommendation it begins to put more weights on vertical component (quality) which, if disclosed, is precise. The latter effect increases the sellers' returns on quality disclosure making the latter more profitable. Eventually, the combined effect of recommender system's inaccuracy on the amount of information disclosed by sellers depends on the value of cost parameter: if the cost of disclosure is high enough, the direct negative effect caused by more intensive competition outweighs the positive effect brought about by the increased return on disclosure and, hence, improving the recommender system precision decreases the amount of information the sellers disclose; for the low cost of disclosure the opposite is true, i.e. increasing the platform's precision increases the amount of information disclosed.

@@

The platform announces the commission rate $\alpha$, and after observing sellers' prices and qualities (if disclosed), should design the recommender policy. The recommender policy specifies functions $r_A(x, p_A, p_B, d_A, d_B, \mathbb{E}[q_A|d_A], \mathbb{E}[q_B|d_B])$ and \newline
$r_B(x, p_A, p_B, d_A, d_B, \mathbb{E}[q_A|d_A], \mathbb{E}[q_B|d_B])$ which represents probabilities that the customer with location $x$ will be recommended the seller $A$ and $B$ respectively. The objective function of the platform is given by \begin{align}\label{pl_profit}
\pi_P = \mathbb{E}\left[\alpha(p_A D_A + p_B D_B) + \gamma CS\right],
\end{align}
where expectation is taken over unknown qualities $q_A, q_B$; $CS$ is a consumer surplus, $\gamma$ represents the platform's degree of consumer-orientedness. I assume that the maximum rate of commission the platform can charge the sellers is $\bar{\alpha} \in (0, 1)$, and $\gamma > \bar{\alpha}$. I need the latter assumption $\gamma > \bar{\alpha}$ since if it does not hold it might be optimal for the platform to completely disregard the consumer surplus and induce as high price as possible to extract the whole consumer surplus. Although the assumption of maximal commission is for convenience it can be justified by assuming that sellers have non-zero outside option, so the platform cannot extract the whole revenue. That is, $\bar{\alpha}$ can be thought of as a maximum commission rate the platform can charge that still guarantees that sellers are willing to sell their goods through the platform.

@@

Making the recommendation system too inaccurate is also not optimal for the platform. It can be easily shown that the platform's profit \eqref{profit_b} tends to minus infinity once $\beta \to 0$. In other words, there exists some optimal level of precision that lies strictly between 0 and 1.
	\section{Discussion}
	\section{Extensions}
	\section{Conclusion}

>>>>

\documentclass[a4paper]{article}
\usepackage[12pt]{extsizes} % 
\usepackage{setspace}
\doublespacing
\usepackage[utf8]{inputenc}
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{patterns}
\usepackage{setspace,amsmath}
\usepackage{mathtools}
\usepackage{pdfpages}
\usepackage{pgfplots}
\usepackage[toc,page]{appendix}
\usepackage{titlesec}
%\usepackage{harvard}
\usepackage[round]{natbib}
\usepackage{pdfpages}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{amsthm}
\usepackage[shortlabels]{enumitem}
\usepackage{tikz}
\usepackage{multirow}
\usetikzlibrary{angles,quotes}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{breakcites}
\interfootnotelinepenalty=10000
\usepackage[makeroom]{cancel}
\usepackage{mathrsfs} % 
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
%\addto\captionsrussian{\renewcommand{\figurename}{Fig.}}
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools} 
\newcommand*{\hm}[1]{#1\nobreak\discretionary{}
{\hbox{$\mathsurround=0pt #1$}}{}}
\usepackage{graphicx}  % 
\graphicspath{{images/}{images2/}}  % 
\setlength\fboxsep{3pt} %  \fbox{} 
\setlength\fboxrule{1pt} % \fbox{}
\usepackage{wrapfig} % 
%\newenvironment{abstract}[0]{\small\rm
%	\begin{center}ABSTRACT
%		\\ \vspace{8pt}
%		\begin{minipage}{5.2in}\smalllineskip
%			\hspace{1pc}}{\end{minipage}\end{center}\vspace{-1pt}}
\newcommand{\prob}{\mathbb{P}}
\newcommand{\norma}{\mathcal{N}}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\summa}{\sum_{i=1}^n}
\usepackage[left=25mm, top=20mm, right=25mm, bottom=20mm, nohead, footskip=10mm]{geometry} % 
\usepackage{tikz} % 
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{definition}[theorem]{Definition}
%\let\cite = \citeasnoun
\title{To run with the hare and hunt with the hounds: Optimal recommendation system with competing sellers. \\ Master Thesis}
\date{}
\author{Danil Fedchenko\thanks{I am very grateful to: Sergei Izmalkov for constant help and support during the work on this project; Marta Troya Martinez for many valuable comments and suggestions. \newline Any remaining errors and inaccuracies are mine.}}
\begin{document} 
	\includepdf[pages=-,pagecommand={},width=\paperwidth]{titul.pdf}
	\maketitle
	\begin{abstract}
		Many e-commerce platforms that connect buyers and sellers employ recommender systems to help customers find products and services. These systems may have several potential effects on strategies of competing sellers: on one hand, more people become aware of products, so sellers may sell more goods and benefit from the presence of the recommender system. On the other hand, at the same time, more people become aware of the competitor seller. The latter effect may intensify the price competition and may hurt sellers but, of course, benefit customers. However, many platforms charge firms for sales and as a result have the stakes in firms profits. Thus, by designing the recommender policy the platform should balance the pro-competitive care about customers and anti-competitive incentives to keep high prices. The main goal of this work is to study this trade-off in details. I am solving for an optimal recommender policy and investigate factors that may affect it.
	\end{abstract}
\newpage
\tableofcontents
\newpage
	\section{Introduction}

	\subsection{Motivation}

		Suppose you came to New York and would like to find a good restaurant to go out tonight. Or you are going to spend your upcoming vacation on the coast of Spain and you need to find a hotel. Or you would like to buy something at your favorite online retailer. How would you proceed? What will be the first thing you interact with?  Before the World Wide Web, to find hotels or restaurants people relied upon guide-books and brochures distributed by travel agents. Those guides, once printed, could quickly become out-of-date in the constantly changing environment, and, as a result, could be criticized for containing misleading information.

@@

In the rows of examples, we should pay the special attention to online retailers such as \textit{Amazon}, \textit{eBay}, \textit{AliExpress} and many others. These platforms stand at the forefront of online Economics, generating huge amounts of money\footnote{e.g. \textit{Amazon}'s gross merchandise value (total value of goods sold on the platform) in 2019 fiscal year was \$335 billion.} and completely transforming the shopping experience for people all other the world. These platforms play roles of intermediaries between buyers and sellers, helping the buyers to find the goods they need. And this process clearly includes making recommendations: which seller to display the buyer when he or she is searching for something.

@@

For example, consider a retailer (such as \textit{Amazon} or \textit{eBay}), these retailers charge sellers commissions for each sale. These commissions usually take the form of a percentage commission \footnote{e.g. \textit{eBay} charges 8\% for each sale}. That means that the retailer obtains a higher profit if the price of the deal is higher. So, one of the questions that could potentially arise then is: should, in this case, the recommender system which \textit{Amazon} employs out of two sellers who sell (almost) substitutable goods recommend the one who has a higher price? Or suppose that \textit{eBay} is thinking on the commission rate it charges, %(now it is about 8\%),
 should the commission be set at the highest possible level that guarantees that sellers do not refrain from using the platform? What if, at the same time, the quality of goods may differ and the sellers may have an option to spend some resources on disclosing this quality (e.g. to make the detailed description or take high-resolution photos). Clearly the higher is the commission the less willing are the sellers to spend money on quality disclosure: cost does not outweigh benefits. But if sellers do not disclose the information this may adversely affect the customers' satisfaction since this may create a mismatch between buyers and sellers: people end up with the good which does not fit them well. Thus, thinking about commission rate the platform should take this aspect into account. Additionally, suppose that the recommendation system is not precise i.e. it sometimes makes mistakes on figuring out the customer's preferences. How does this inaccuracy affect the behavior (price setting) of competing sellers and how does it interact with their incentives to disclose the quality of their goods? What should be the optimal commissions and recommender policy in this case? I find all those issues interesting both from pure theoretical and practitioner's standpoints and explore them in this work.
 So, to summarize this subsection let me list the questions I will address.
 \begin{itemize}
 	\item How does the presence of the recommender system which has stakes in sellers' profits affect competition and equilibrium behavior of sellers?
 	\item How does the rate of commission the platform charges sellers affect sellers' incentives to disclose information about their goods? What is the optimal rate of commission from the platform's standpoint?
 	\item How does the recommender system's precision affect competition and equilibrium behavior? And what should be the optimal precision?
 \end{itemize}

 	\subsection{Overview of the Model and Results}
	To address these questions I build a theoretical one-period model. I consider a unit mass of heterogeneous customers whose preferences are summarized by the point on this unit line. At the extremes of the unit interval, there are two sellers. Customers demand one good and derive utility upon consuming the good but bear ``transportation'' cost by purchasing. This cost can be interpreted as the measure of quality of fit: how well the product fits the particular customer. The latter allows to treat the location of the customer as the customer's taste regarding the two goods offered by sellers: closer the customer is to the seller $A$ -- better the good of seller $A$ fits this customer, other things being equal.

@@

In the extension of the baseline model, I allow for the not perfectly precise recommender system, or in other words, I allow for some noise in evaluating customers' location. Namely, I assume that the signal, the platform receives reveals the true location of the customer only with some probability $\beta$, and with probability $1 - \beta$ the signal follows a uniform distribution. This has several consequences: first of all, clearly the platform should adjust its recommender strategy incorporating this inaccuracy. This adjustment manifests itself in the way how the platform treats and processes the signal regarding the location, now the platform takes into consideration that the signal could potentially be wrong. In this case, the best prediction of the customer's location the platform could made is simply an average location (since I model customers' location as uniform $(0, 1)$ random variable, an average location is $\frac{1}{2}$) . The latter effectively increases the share of customers in the middle of the unit interval, increasing incentives for sellers to undercut the competitor and to get access to this increased demand. Thus, the direct effect of the signal's inaccuracy intensifies the competition between sellers. This decreases the sellers' profits and as a result, decreases sellers' incentives to reveal the quality. At the same time, the recommender system's inaccuracy increases the attention the platform pays to the quality of the good when it makes recommendations: since the platform assumes that horizontal component (location) may be measured imprecisely, making a recommendation it begins to put more weights on vertical component (quality) which, if disclosed, is precise. The latter effect increases the sellers' returns on quality disclosure, making the latter more profitable. Eventually, the combined effect of recommender system's inaccuracy on the amount of information disclosed by sellers depends on the value of cost parameter: if the cost of disclosure is high enough, the direct negative effect caused by more intensive competition outweighs the positive effect brought about by the increased return on disclosure and, hence, improving the recommender system precision decreases the amount of information the sellers disclose; for the low cost of disclosure the opposite is true, i.e. increasing the platform's precision increases the amount of information disclosed.

@@

The platform announces the commission rate $\alpha$, and after observing sellers' prices and qualities (if disclosed), should design the recommender policy. The recommender policy specifies functions $r_A(x, p_A, p_B, d_A, d_B, \mathbb{E}[q_A|d_A], \mathbb{E}[q_B|d_B])$ and \newline
$r_B(x, p_A, p_B, d_A, d_B, \mathbb{E}[q_A|d_A], \mathbb{E}[q_B|d_B])$ which represents probabilities that the customer with location $x$ will be recommended the seller $A$ and $B$ respectively. The objective function of the platform is given by \begin{align}\label{pl_profit}
\pi_P = \mathbb{E}\left[\alpha(p_A D_A + p_B D_B) + \gamma CS\right],
\end{align}
where expectation is taken over unknown qualities $q_A, q_B$; $CS$ is a consumer surplus, $\gamma$ represents the platform's degree of consumer-orientedness. I assume that the maximum rate of commission the platform can charge the sellers is $\bar{\alpha} \in (0, 1)$, and $\gamma > \bar{\alpha}$. I need the latter assumption $\gamma > \bar{\alpha}$ to rule out possible cases which lie beyond the focus of this work: if this assumption does not hold it might be optimal for the platform to completely disregard the consumer surplus and induce as high price as possible to extract the whole consumer surplus. Although the assumption of maximal commission is for convenience it can be justified by assuming that sellers have non-zero outside option, so the platform cannot extract the whole revenue. That is, $\bar{\alpha}$ can be thought of as a maximum commission rate the platform can charge that still guarantees that sellers are willing to sell their goods through the platform.

@@

Making the recommendation system too inaccurate is also not optimal for the platform. It can be easily shown that the platform's profit \eqref{profit_b} tends to minus infinity once $\beta \to 0$. In other words, there exists some optimal level of precision that lies strictly between 0 and 1. To find this optimal precision may be an interesting problem, although to keep the paper to an appropriate length I leave this for the future research.
	\section{Extensions}
	Being rather simple, the model I considered in the previous sections allows for several extensions. In this section, I firstly discuss potential ways of extending the existing model. Then I suggest some ideas which might render the model more sophisticated. The latter, in principle, may give us new insights which cannot be seen in this work.

	First of all, it is worth studying what happens if the assumption on the common component of agents' utilities, $V$ does not hold. In this case, markets may not be fully covered in the type of equilibrium I considered. This fact may affect the strategic behavior of sellers, as a result, outcomes of interaction can change substantially.

	Moreover, in this work, I demonstrated that perfect precision is not optimal for the recommender system, although I did not explore what is the optimal precision. To find an optimal precision and investigate which factors affect it -- is another interesting possibility for future work.

	Another appealing direction is to endogenise $\gamma$ by allowing the platform to charge buyers for receiving recommendations (subscription fee)\footnote{I thank Sergey Kovbasyuk for this suggestion}. In reality,  there are many platforms which indeed charge subscription fees providing customers with recommendations in return. In this case, the platform gets a tool which enables it to directly affect consumer surplus. So, it would be very interesting to see how, in this case, the optimal policy: recommendations, sellers commissions, buyers commissions would look like.

	In my model sellers simultaneously undertake strategic actions, although in real life many sellers may, in the first place, observe actions of their competitors. Hence, it can be interesting to investigate how robust are theoretical results obtained in this work to the change of mode of competition between sellers. In particular, one potential extension in this direction may include considering Stackelberg-like leader-follower mode of competition \footnote{I thank Shlomo Weber for this suggestion}. Additionally, it may be interesting to follow \cite{levin2009quality} and consider the cartel model (i.e. allow sellers to collude and undertake strategic actions cooperatively).

	Finally, it could be interesting to test and validate the kind of theoretical predictions, I made in this work, empirically. Although it can be difficult to obtain data on exact recommendation strategies different platform use, data on commissions can be found relatively easily.
	\section{Conclusion}
	Recommender systems became widespread in the last several decades. And although Computer and Data Scientists advanced a lot in our abilities to pin down users' preferences which allows us to make personal recommendations. It was clear that these abilities of platforms to make recommendations might substantially transform the information structure of the interaction between economic agents. The latter suggests that the platform should judiciously choose its recommendation policy (and maybe even not always recommend an alternative which is the best for a user from his or her own standpoint\footnote{In my model this indeed happens. Under some conditions, there may exist users who strictly prefer one seller to another while are recommended the latter one simply because this guarantees the platform higher profit from commissions.}). This work belongs to the strand of economic literature which explores and suggests how the optimal recommendation policy should look like and what factors may influence it.

	Turning to the set of questions I listed in the introduction, in the work I derived the optimal recommendation policy. I demonstrate that the presence of a recommender system which has stakes in sellers' profit softens competition. Moreover, the effect is stronger the lower is the degree of platform's consumer orientedness (which I denoted as $\gamma$). This parameter plays a crucial role in determining the effect of commissions on the amount of information which sellers disclose. I showed that if $\gamma$ is high then high commission results in less information being disclosed by sellers in equilibrium. While for small $\gamma$'s the relation goes in another direction i.e. an increase in commission increases the amount of disclosed information. This result stems from the interplay between two counteracting forces: an increase in commission decreases the sellers' profits directly; at the same time, this increases the platform's stakes in profit and as a result softens competition. The implication of this result is that for large $\gamma$ the platform should charge sellers the smallest possible commission.

As for precision, I demonstrated that low precision weakens the effect of the presence of the recommender system. In other words, other things being equal, lower precision means harsher competition. This happens since the imprecision effectively increases the share of ``average'' customers who are the most desirable target the competing sellers would like to compete for. The imprecision also affects the amount of information the sellers disclose in equilibrium. However, the direction of this effect depends on the cost of disclosure: for low cost making the recommender system more precise may increase the amount of information disclosed, while for high cost the result is the opposite. The reason is that imprecision makes it optimal for the platform to put more weight on disclosed information (since this information is precise). This motivates sellers to disclose the information, partially offsetting the direct negative effect of imprecision brought about by harsher competition and lower profits. The last thing I showed in this paper is that some imprecision, in fact, can be optimal for the platform. The intuition behind this result is the following: on one hand, the imprecision directly harms consumer surplus (since mismatch between seller and buyer is more probable); but at the same time, perfect precision makes the competition too soft, and this negative (for consumer surplus) effect outweighs benefits caused by the absence of mismatch. In other words, it is optimal sometimes to ``sacrifice'' some customers (and recommend them not the best alternative for them) in order to intensify competition between sellers and benefit everybody (except for sellers) by lower prices.

	The theoretical model considered in this work is, of course, only a simplification of reality. It can be extended further to incorporate more real-life features of the type of interactions I considered. However, I believe the results I obtained can give practitioners insights about the thing they should pay attention once designing the optimal recommendation policy.
